% ftp://ftp.funet.fi/pub/TeX/CTAN/macros/latex/contrib/moderncv/examples/template.tex
\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{blue}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}

% page margins
\usepackage[scale=0.75]{geometry}

% personal data
\firstname{Juho}
\familyname{Vepsäläinen}
%\title{Curriculum Vitae}
%\address{street and number}{Jokutie 123, 12345 Perähikiä, Finland}
%\mobile{+358~123456789}
%\phone{}
%\fax{}
\email{juho.vepsalainen@koodilehto.fi}
\homepage{www.nixtu.info}
%\extrainfo{}
%\photo[64pt][0.4pt]{photo.jpg}
%\quote{Some quote}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2005--2011}{Master of Science}{University of Jyväskylä}
{Software engineering (open source), mathematics, growth venturing}{}{}
\cventry{2001--2004}{Abitur/Technician (electronics)}
{Jyväskylä Educational Consortium}
{Electronics and general education (English etc.)}{}{}

\section{Experience}

\cventry{2011--}{Freelancer}{Koodilehto co-op}{}{}
{Web development (Django, MVC3, Ruby on Rails) and startup work.}
\cventry{2011 Summer}{Software Designer}{Fudeco Oy}{}{}
{Django and jQuery development for a local media consortium.}
\cventry{2010--2011}{Contractor}{Mixart New Media LLC}{}{}
{Implemented HTML5 Canvas based drawing application.}
\cventry{2008--2010}{3D Designer, Programmer, Research Assistant}{University of Jyväskylä}{}{}
{3D modeling (Blender) and development (Django, AS2, MediaWiki) for research purposes.}
\cventry{2005-2009}{Volunteer}{Blender3D}{}{}
{Wiki maintenance, software development (patches, patch reviewing, design).}

\section{Languages}

\cvitemwithcomment{English}{Excellent}{High grades (both abitur and university).}
\cvitemwithcomment{Finnish}{Excellent}{Native.}

\section{Computer skills}

\cvdoubleitem{Programming Languages}{JavaScript, Python, C, PHP, Lua, C\#, Ruby, Haskell, ...}
{Version Control}{git, Subversion, Mercurial}
\cvdoubleitem{Technologies}{Django, MediaWiki, jQuery, Node.js, ...}
{Applications}{Blender3D, vim, GIMP, ...}

\section{Interests}

\cvitem{Art}{I enjoy studying and creating art and like to draw.}
\cvitem{Open Source Development}{I maintain a wide range of projects of my own
at \url{www.github.com/bebraw}.}
\cvitem{Sports}{I like endurance sports and cycling in particular.}

\end{document}
